Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2020-04-25 paper/main.tex
fixes broken sentence for normalised rank

A result summary (Table~\ref{table:output_result}) has \(N\) rows
because each row contains information for each strategy that participated in the
tournament. The information includes the strategy's rank, median score, the rate
with which the strategy cooperated $(C_r)$, its match win count, and the
probability that the strategy cooperated in the opening move. Moreover, the
probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
and the rate of which the strategy cooperated after each state. The \textbf{normalised rank}
feature that is manually added. The rank \(R\) of a given.
strategy can vary between 0 (first) and \(N-1\) (last). Thus, the normalised rank,
denoted as $r$, is calculated as a strategy's rank divided by \(N - 1\).

>>>>

A result summary (Table~\ref{table:output_result}) has \(N\) rows
because each row contains information for each strategy that participated in the
tournament. The information includes the strategy's rank, median score, the rate
with which the strategy cooperated $(C_r)$, its match win count, and the
probability that the strategy cooperated in the opening move. Moreover, the
probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
and the rate of which the strategy cooperated after each state. The \textbf{normalised rank}
is a feature that has been manually added to the result summary. The rank \(R\) of a given
strategy can vary between 0 (first) and \(N-1\) (last), and thus the normalised rank,
denoted as $r$, is calculated as a strategy's rank divided by \(N - 1\).
